---
title: "Clustere differential composition analysis"
author: "Adapted from cluster differential composition analysis by Boying Gong"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
# Rscript -e "rmarkdown::render('cluster_visualization.Rmd')"
```


```{r}
library(dplyr)
library(uwot)
library(reshape2)
library(Seurat)
library(ggplot2)
library(NMF)
library(clusterExperiment)
library(readr)
library(stringr)
library(MASS)
library(RColorBrewer)
library(umap)

ddir <- "E:/Human - 10 clusters/yale-method/Archive2/composition from Hao/"
load(paste0(ddir, "Our41_meta.Rda"))

meta <- meta[-which(meta$donor %in% c(203, 218)), ]

cell_identity = read.csv(paste0(ddir, "cell_identity.csv"))[,1:3]
meta$identity = cell_identity$Identities[match(meta$ID, cell_identity$Cluster)]
num_cell = matrix(data = NA, nrow = length(unique(meta$donor)), ncol = 41)
rownames(num_cell) = unique(meta$donor)
colnames(num_cell) = 1:41
for(i in rownames(num_cell)){
  for(j in 1:41){
    num_cell[i,j] = sum(meta$ID == j & meta$donor == i)
  }
}

prop_cell = num_cell/rowSums(num_cell)
#prop_cell <- t(read_csv(paste0(ddir,"prop_cell.csv")))[-1,1:36]
#cell_ident = read_csv(paste0(ddir,"new36_ident.csv"))[,1:3]
#cell_ident$Group = c(rep("lymphoid", 17), rep("myeloid",19))
colnames(num_cell) = colnames(prop_cell)  = cell_identity$Identities
meta_use = unique(meta[,1:2])
rownames(meta_use) = meta_use$donor
meta_use$dis = factor(meta_use$dis, 
                      levels = c("NML", "AD1", "AE", "Pso", "LP", "BP"))
meta$new_level = ifelse(meta$dis == "NML", "NML", "Rash")
```

# All cluster

## Cluster composition

The following plots shows the cluster frequency and proportion for each patient and the disease type. 


```{r}
#plot_df$ident = cell_ident$Identity[match(plot_df$seurat_clusters, cell_ident$d)]
#plot_df$ident <- factor(plot_df$ident, levels = cell_ident$Identity)
meta$identity <- factor(meta$identity, levels = cell_identity$Identities)
barplot(table(meta$identity), las = 2)


  
```

```{r}

SampleInCondition <- c()
counter <- c(0, 0, 0, 0, 0, 0, 0)
for (i in meta_use$dis){
    idx <- which(i == unique(meta_use$dis))
    counter[idx] = counter[idx] + 1
    SampleInCondition <- c(SampleInCondition, counter[idx])
}
meta_use$SampleInCondition <- SampleInCondition

```

```{r, out.width="100%", results='asis'}
sort_order = names(sort(-table(meta$identity)))
cell_total = rowSums(num_cell)
pvals <- list()
zvals <- list()
pct_df <- list()
odds <- list()
for (c in levels(meta$identity)){
    # cat("\n\n### Cluster", c, "\n\n")

    current_meta <- as.data.frame(meta_use)
    current_meta$this_cluster <- num_cell[,c]
    current_meta$n <- cell_total
    current_meta$ClusterProp <- num_cell[,c] / cell_total

    current_meta <- as.data.frame(current_meta)
    current_meta$CellType <- c
    
    
#    current_meta <- as.data.frame(current_meta %>% 
#        group_by(Treatment, Age, Batch) %>% 
#        summarise(this_cluster = sum(this_cluster), n = sum(n)))
    
    # cat("\n#### Significance level of the age/injury effect.\n")
#current_meta$Batch <- factor(current_meta$Batch, levels = c("3", "1", "2"))
    current_meta$dis = relevel(factor(current_meta$dis), "NML")
   current_meta =  current_meta[current_meta$dis%in% c("NML", "AD1", "AE", "Pso", "LP", "BP"),]
   current_meta$new_level = ifelse(current_meta$dis == "NML", "NML", "Rash")

       pct_df[[c]] <- current_meta

    fit <- glm(
        cbind(this_cluster, n-this_cluster)~dis,
        data=current_meta, family=quasibinomial())
    fit_all <- glm(cbind(this_cluster, n-this_cluster)~new_level,
        data=current_meta, family=quasibinomial())
    res <- summary(fit)$coefficients
    res_all <- summary(fit_all)$coefficients
    tmp <- c(res[c("disAD1", "disAE", "disPso"), "Pr(>|t|)"], res_all["new_levelRash", "Pr(>|t|)"])
    names(tmp) <- c("AD vs N", "AE vs N", "Pso vs N", "Rash vs N")
    pvals[[c]] <- tmp
    tmp <- c(res[c("disAD1", "disAE", "disPso"), "t value"], res_all["new_levelRash", "t value"])
    names(tmp) <- c("AD vs N", "AE vs N", "Pso vs N", "Rash vs N")
    zvals[[c]] <- tmp
    tmp <- log2(exp(c(res[c("disAD1", "disAE", "disPso"), "Estimate"], res_all["new_levelRash", "Estimate"])))
    names(tmp) <- c("AD vs N", "AE vs N", "Pso vs N", "Rash vs N")
    odds[[c]] <- tmp
}
```



```{r, results="asis", fig.width=12, fig.height=10}
pct_df <- do.call("rbind", pct_df)
```



```{r, fig.width=12, fig.height=6, out.width='90%'}
pct_df$CellType = factor(pct_df$CellType, levels = c("Tcm", "Trm1", "eTreg1", "Trm2","CTLex","CTLem","Tet","Tmm1","ILC/NK","NK","Trm3", "cmTreg","Tmm2","eTreg2","Tmm3","ILC2","Tn","moDC1","LC1","InfMono","Mac1","Mono","LC2","moDC2","moDC3","DC1","DC2","LC3","Mac2","Plasma",
                                                  "B","Mac3","DC3","migDC","Mac4","Mast","Trm-c","Treg-c","Mast-c","ILC/NK-c","CTL-c"))
pct_df$dis = relevel(factor(pct_df$dis), "NML")
ggplot(data=pct_df, aes(x=SampleInCondition, y = ClusterProp, fill=CellType)) +
  geom_bar(stat="identity") + 
  facet_grid(~dis, drop = FALSE) +
  xlab("Sample") + ylab("Proportion") +
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Paired"))(41)) +
  theme_bw()+
  theme(legend.position="bottom")
  guides(fill=guide_legend(nrow=3,byrow=TRUE))

```


## Composition dissimilarity


### proportion (full)


```{r}
darkcols <- brewer.pal(9, "Set1")
colfunc <- colorRampPalette(c("white", "blue4"))
dist_mat = as.matrix(dist(prop_cell, upper = T, diag = T))
aheatmap(dist_mat, color = colfunc(51),
         annCol = list(Condition = meta_use$dis),
         annColors = list(Condition = darkcols),
         Colv = FALSE, Rowv = FALSE, main = "Distance Matrix Heatmap for full data proportion")
```

```{r mdsFull_prop}
fit_mds <- isoMDS(dist_mat, k = 2)
colnames(fit_mds$points) <- c("Coordinate1", "Coordinate2")
mds_df <- cbind(meta_use, fit_mds$points)



ggplot(mds_df, aes(x = Coordinate1, y = Coordinate2, 
                                color = dis)) + geom_point() + 
  scale_color_manual(values=darkcols) + 
  theme_bw() + 
  geom_text(aes(label=donor),hjust=0, vjust=0)
```

```{r umap_prop}
fit_10_mds <- isoMDS(dist_mat, k = 10)
colnames(fit_10_mds$points) <- paste0("Coordinate", 1:10)


umap_df <- umap(fit_10_mds$points)$layout
colnames(umap_df) <- paste0("umap", 1:2)
mds_umap_df <- cbind(meta_use, umap_df)
ggplot(mds_umap_df, aes(x = umap1, y = umap2, 
                                color = dis)) + geom_point() + 
  scale_color_manual(values=darkcols) + 
  theme_bw() + 
  geom_text(aes(label=donor),hjust=0, vjust=0)

```


### proportion (no 203)

In this subsection, we take off the patient 203

```{r}
dist_mat = as.matrix(dist(prop_cell[-33,], upper = T, diag = T))
aheatmap(dist_mat, color = colfunc(51),
         annCol = list(Condition = droplevels(meta_use$dis[-33])),
         annColors = list(Condition = darkcols),
         Colv = FALSE, Rowv = FALSE, main = "Distance Matrix Heatmap without 203")
```

```{r mdsFull}
fit_mds <- isoMDS(dist_mat, k = 2)
colnames(fit_mds$points) <- c("Coordinate1", "Coordinate2")
mds_df <- cbind(meta_use[-33,], fit_mds$points)



ggplot(mds_df, aes(x = Coordinate1, y = Coordinate2, 
                                color = dis)) + geom_point() + 
  scale_color_manual(values=darkcols) + 
  theme_bw() + 
  geom_text(aes(label=donor),hjust=0, vjust=0)
```

```{r umap}
fit_10_mds <- isoMDS(dist_mat, k = 10)
colnames(fit_10_mds$points) <- paste0("Coordinate", 1:10)


umap_df <- umap(fit_10_mds$points)$layout
colnames(umap_df) <- paste0("umap", 1:2)
mds_umap_df <- cbind(meta_use[-33,], umap_df)
ggplot(mds_umap_df, aes(x = umap1, y = umap2, 
                                color = dis)) + geom_point() + 
  scale_color_manual(values=darkcols) + 
  theme_bw() + 
  geom_text(aes(label=donor),hjust=0, vjust=0)

```



```{r, results="asis"}
pvals <- do.call("rbind", pvals)
zvals <- do.call("rbind", zvals)
odds <- do.call("rbind", odds)
# knitr::kable(cbind(pvals, sign(zvals)))
```


## differential composition -- count model (Quasi-binomial)

Denote $N_i^j$ as the number of cells in sample $i$, cluster $j$. And $N_i = \sum_j N_i^j$ as the total number of cells in sample $i$.

In this section, we applied quasi-binomial model, which is similar to binomial count models $N_i^j\sim Binom(N_i, p_i^j)$, but has an extra parameter $\phi$ that attempts to describe additional variance in the data that cannot be explained by a Binomial distribution alone. 



Here we applied the differential composition analysis for disease type vs normal. In the future, we may change reference group to test among different disease types.

In the following plots, each row shows a cluster, and each graph shows a comparison: A vs. B: Positive (1) means the cell type is more abundant in A; negative (-1) indicates the opposite.


From the plot, we can see different clusters might receive different effect on conditions.

```{r, results="asis", fig.width=10, fig.height=7}
plot_pvals <- function(pvals, zvals){
    pvals_adj <- p.adjust(pvals, method = "BH")
    vis_pvals_adj <- abs(log10(pvals_adj+1e-10)) * sign(zvals)
    knitr::kable(  vis_pvals_adj  )
    vis_pvals_adj <- as.data.frame(vis_pvals_adj)
    vis_pvals_adj$CellType = rownames(vis_pvals_adj)
    vis_pvals_adj$CellType <- factor(vis_pvals_adj$CellType, levels = cell_identity$Identities)
#    levels(vis_pvals_adj$CellType) <- 1:41
    vis_pvals_adj = melt(vis_pvals_adj)
    colnames(vis_pvals_adj)[2:3] = c("Comparison", "LogPAdj")
    vis_pvals_adj$IsSig = abs(vis_pvals_adj$LogPAdj) >= abs(log10(0.05+1e-10))
    
    p <- ggplot(vis_pvals_adj) + 
      geom_bar(stat = "identity", aes(x = CellType, y = LogPAdj, fill = IsSig)) + 
      facet_wrap(.~Comparison, ncol = 2) + coord_flip() +
      geom_hline(yintercept=c(-log10(0.05+1e-10), 
                              log10(0.05+1e-10)), 
                 linetype="dotted") +
      scale_fill_manual(values = c("gray", "red4")) + 
      theme(legend.position = "none") +
      theme_bw()
    
    print(p)
}

plot_coef <- function(coef, pvals, coef_name){
    vis_coef <- coef
    pvals_adj <- p.adjust(pvals, method = "BH")
    vis_pvals_adj <- abs(log10(pvals_adj+1e-10))
    knitr::kable(  vis_coef  )

    
    vis_coef <- as.data.frame(vis_coef)
    vis_coef$CellType = rownames(vis_coef)
    vis_coef$CellType <- factor(vis_coef$CellType, levels = cell_identity$Identities)
    #vis_coef$CellType <- factor(vis_coef$CellType, levels = 1:41)
    vis_coef = melt(vis_coef)
    colnames(vis_coef)[2:3] = c("Comparison", "coefs")
    vis_coef$IsSig = abs(vis_pvals_adj) >= abs(log10(0.05+1e-10))

  
    
    o <- ggplot(vis_coef) + 
      geom_bar(stat = "identity", aes(x = CellType, y = coefs, fill = IsSig)) + 
      facet_wrap(.~Comparison, ncol = 2) + coord_flip() +
      geom_hline(yintercept=c(-1,1), 
                 linetype="dotted") +
      scale_fill_manual(values = c("gray", "red4")) + 
      theme(legend.position = "none") +
      theme_bw() +ylab(coef_name)
    

    
    return(o)
}


plot_pvals(pvals, zvals)
print(plot_coef(odds, pvals, "log2OddsRatio"))

```




```{r}
library(compositions)
data(SimulatedAmounts)
```

```{r}
tmp <- meta[, c("donor", "dis", "identity")] %>%
  group_by(donor, dis, identity) %>%
  summarise(counts = n())
cluster_comp <- dcast(tmp, donor+dis~identity)
cluster_comp[is.na(cluster_comp)] <- 0.5
y <- acomp(cluster_comp[, -c(1:2)])
y_rcomp <- rcomp(cluster_comp[, -c(1:2)])
x <- cluster_comp[, c(1:2)]
```



## Differential Composition - Gaussian Model


In this section, we tried the weighted linear models on the log celltype compositions $(\log \frac{N_i^1}{N_i}, \cdots, \log \frac{N_i^k}{N_i})$, using 1/sd as weight. If the patient in cluster i has 0 count, we set its count to be 0.5 for downstream analysis computation.

For each cell type k, let $p_{ik} = \frac{N_i^k}{N_i}, z_{ik} = \log \frac{N_i^k}{N_i}$ for patient i.

We define $\bar P_{Nk} = \frac{1}{n_N}\sum_{i \in N} \frac{N_i^k}{N_i}, \ \bar P_{Dk} = \frac{1}{n_D}\sum_{i \in D} \frac{N_i^k}{N_i}, \ \bar Z_{Nk} = \frac{1}{n_N}\sum_{i \in N} \log \frac{N_i^k}{N_i},\  \bar Z_{Dk} = \frac{1}{n_D}\sum_{i \in D} \log \frac{N_i^k}{N_i}$ for normal and disease group, where $n_N, n_D$ are the number of patients in normal and disease group respectively.

Here we also plot the log-fold change $\log\frac{\bar P_{Dk}}{\bar P_{Nk}}, \bar Z_{Dk} - \bar Z_{Nk}$, and log odds ratio $\log\frac{\bar P_{Dk}/(1-\bar P_{Dk})}{\bar P_{Nk}/(1-\bar P_{Nk})},\log\frac{exp(\bar Z_{Dk})/(1-exp(\bar Z_{Dk}))}{exp(\bar Z_{Nk})/(1-exp(\bar Z_{Nk}))}$ for each cell type k.

In the following plots, logP refers to $z_{ik}$ and P refers to $p_{ik}$


The following figure shows the variances of the normalized composition across samples for each cluster.

```{r, fig.width=7, fig.height=6, out.width='70%'}
library(clusterExperiment)
par(mar=c(10,2,2,2))
barplot(diag(var(y)),las=2)
```


```{r, results="asis", fig.width=10, fig.height=7}
pct_df$new_count =  ifelse(pct_df$this_cluster == 0, 0.5, pct_df$this_cluster)
pct_df$new_prop = pct_df$new_count/pct_df$n
pct_df$var = (pct_df$new_prop*(1-pct_df$new_prop))/(pct_df$n*pct_df$new_prop^2)
pct_df$sd = sqrt(pct_df$var)

#pct_df$new_level = factor(ifelse(pct_df$dis == "NML", "NML", "Rash"))
pvals_prop = list()
zvals_prop = list()
odds_prop = list()
foldchange = list()
logfoldchange_prop = list()
logodds = list()

for(c in levels(pct_df$CellType)){
  current_meta = pct_df[pct_df$CellType == c,]
  current_meta = current_meta[current_meta$dis %in% c("NML", "AD1", "AE", "Pso", "LP", "BP"),]
  fit = lm(log(new_prop) ~ dis, 
              data = current_meta, 
              weights = 1/sd)
  fit_all = lm(log(new_prop) ~ new_level, 
              data = current_meta, 
              weights = 1/sd)
    res <- summary(fit)$coefficients
    res_all <- summary(fit_all)$coefficients
    tmp <-  c(res[c("disAD1", "disAE", "disPso", "disLP", "disBP" ), "Pr(>|t|)"], res_all["new_levelRash", "Pr(>|t|)"])
    names(tmp) <- c("AD vs N", "AE vs N", "Pso vs N","LP vs N", "BP vs N", "Rash vs N")
    pvals_prop[[c]] <- tmp
    tmp <-  c(res[c("disAD1", "disAE", "disPso", "disLP", "disBP"), "t value"], res_all["new_levelRash", "t value"])
    names(tmp) <- c("AD vs N", "AE vs N", "Pso vs N","LP vs N", "BP vs N",  "Rash vs N")
    zvals_prop[[c]] <- tmp
#    Pn = sum(current_meta$this_cluster[current_meta$new_level == "NML"])/sum(current_meta$n[current_meta$new_level == "NML"])
#    Pd = sum(current_meta$this_cluster[current_meta$new_level == "Rash"])/sum(current_meta$n[current_meta$new_level == "Rash"])
    logpn = res[1,1]
    logpAD = res["disAD1",1] + res[1,1]
    logpAE = res["disAE",1] + res[1,1]
    logpPso = res["disPso",1] + res[1,1]
    logpLP = res["disLP",1] + res[1,1]
    logpBP = res["disBP",1] + res[1,1]
    logpr = res_all[1,1]+ res_all[2,1]

    pn = mean(current_meta$new_prop[current_meta$dis == "NML"])
    pr = mean(current_meta$new_prop[current_meta$new_level == "Rash"])
    pAD = mean(current_meta$new_prop[current_meta$dis == "AD1"])
    pAE = mean(current_meta$new_prop[current_meta$dis == "AE"])
    pPso = mean(current_meta$new_prop[current_meta$dis == "Pso"])
    pLP = mean(current_meta$new_prop[current_meta$dis == "LP"])
    pBP = mean(current_meta$new_prop[current_meta$dis == "BP"])
    tmp = c(log2(pAD/pn), log2(pAE/pn), log2(pPso/pn), log2(pLP/pn), log2(pBP/pn), log2(pr/pn))
    names(tmp) = c("AD vs N", "AE vs N", "Pso vs N", "LP vs N", "BP vs N", "Rash vs N")
    logfoldchange_prop[[c]] = tmp
    tmp = c(log2(pAD/(1-pAD)/(pn/(1-pn))), log2(pAE/(1-pAE)/(pn/(1-pn))), log2(pPso/(1-pPso)/(pn/(1-pn))), log2(pLP/(1-pLP)/(pn/(1-pn))), 
            log2(pBP/(1-pBP)/(pn/(1-pn))), log2(pr/(1-pr)/(pn/(1-pn))))
    names(tmp) = c("AD vs N", "AE vs N", "Pso vs N", "LP vs N",  "BP vs N", "Rash vs N")
    odds_prop[[c]] = tmp
    tmp = log2(exp(c(res[c("disAD1", "disAE", "disPso", "disLP", "disBP"), "Estimate"], res_all["new_levelRash", "Estimate"])))
    names(tmp) = c("AD vs N", "AE vs N", "Pso vs N", "LP vs N", "BP vs N", "Rash vs N")
    foldchange[[c]] = tmp
    tmp = c(log2(exp(logpAD)/(1-exp(logpAD))/(exp(logpn)/(1-exp(logpn)))),
            log2(exp(logpAE)/(1-exp(logpAE))/(exp(logpn)/(1-exp(logpn)))),
            log2(exp(logpPso)/(1-exp(logpPso))/(exp(logpn)/(1-exp(logpn)))),
            log2(exp(logpLP)/(1-exp(logpLP))/(exp(logpn)/(1-exp(logpn)))),
            log2(exp(logpBP)/(1-exp(logpBP))/(exp(logpn)/(1-exp(logpn)))),
            log2(exp(logpr)/(1-exp(logpr))/(exp(logpn)/(1-exp(logpn)))))
    names(tmp) = c("AD vs N", "AE vs N", "Pso vs N", "LP vs N", "BP vs N", "Rash vs N")
    logodds[[c]] = tmp
}

pvals_prop = do.call(rbind, pvals_prop)
zvals_prop = do.call(rbind, zvals_prop)
logodds = do.call(rbind, logodds)
foldchange = do.call(rbind, foldchange)
odds_prop = do.call(rbind, odds_prop)
logfoldchange_prop = do.call(rbind, logfoldchange_prop)

library("multiHiCcompare")
        
#plot_pvals(pvals_prop, zvals_prop)

print(plot_coef(logodds, pvals_prop, "log2OddsRatio_logP"))
print(plot_coef(foldchange, pvals_prop, "log2-foldchange_logP"))
print(plot_coef(odds_prop, pvals_prop, "log2OddsRatio_P"))
print(plot_coef(logfoldchange_prop, pvals_prop, "log2-foldchange_P"))


```




```{r, eval = F}
save(foldchange, pvals_prop, cell_identity, meta, file = "41cluster_data_yale_no203_218.Rda")

```

